---
title: "Model"
output:
  html_document:
    df_print: paged
---

This Shiny app is to demo our machine learning model. It can quikly upload test data and get amazed by your nice model. In this notebook, we will build a regularized logistic regression that predicts whether microchips from a fabrication plant passes quality assurance (QA). During QA, each microchip goes through various tests to ensure it is functioning correctly. Suppose you are the product manager of the factory and you have the test results for some microchips on two diffeerent tests. From these two tests, you would like to determine whether the microchips should be accepted or rejected. Next, we will save the model and build a shiny app and test the app by uploading test data. Finally, we will download the data we uploaded with predictions using the machine learning model we buit below. The data is from the famous Machine Learning Coursera Course by Andrew Ng. The data can be downloaded from [here](http://datascience-enthusiast.com/data/ex2data2.txt).


**We will use the caret package for cross-validation and grid search**
```{r, message=FALSE}
library(readr)
library(caret)
library(tidyverse)
```

## Import Packages
```{python}
import pandas as pd
import numpy as np
from warnings import simplefilter
simplefilter(action='ignore', category=FutureWarning)
```


## Read data
```{python}
data = pd.read_csv("Consumer_Complaints_lemma.csv")
data.head()
```

```{python}
#writing partial data into csv as test set
testset = pd.DataFrame(data, columns=['Lemmatized', 'Product'])[2001:3000]
testset.to_csv(r'/Users/tinganlai/Documents/GitHub/PraticumProject-/rshiny/test.csv',  index=None, header=True)




#df.to_csv(r'Path where you want to store the exported CSV file\File Name.csv')
```



```{python}
#only use first 500 rows to try
df1 = pd.DataFrame(data, columns=['Lemmatized','Product'])[1:2000]
df1.head()
```



```{python}
## use Multi-Class Log-Loss as evaluation metric
def multiclass_logloss(actual, predicted, eps=1e-15):
    # Multi-classification by Logarithmic Loss Metric
    # param actual: actual target classes
    # param predicted: result matrix of classification prediction, each category has a probability
    
    # Convert 'actual' to a binary array if it's not already:
    if len(actual.shape) == 1:
        actual2 = np.zeros((actual.shape[0], predicted.shape[1]))
        for i, val in enumerate(actual):
            actual2[i, val] = 1
        actual = actual2

    clip = np.clip(predicted, eps, 1 - eps)
    rows = actual.shape[0]
    vsota = np.sum(actual * np.log(clip))
    return -1.0 / rows * vsota


```

```{r}
library(reticulate)
py_install("sklearn")
```


```{python}
# transfer text labels (y) to integers 
from sklearn import preprocessing, decomposition, model_selection, metrics, pipeline

lbl_enc = preprocessing.LabelEncoder()
y = lbl_enc.fit_transform(df1.Product.values)

print(y.shape)
```

```{python}
# train-test set split
from sklearn.model_selection import train_test_split

xtrain, xtest, ytrain, ytest = train_test_split(df1.Lemmatized.values, y, 
                                                  stratify=y, 
                                                  random_state=40, 
                                                  test_size=0.1, shuffle=True)
print (xtrain.shape)
print (xtest.shape)

```





```{python}
# build basic model：
# TF-IDF transformation
import pickle
from sklearn.feature_extraction.text import TfidfVectorizer, CountVectorizer

tfv = TfidfVectorizer(min_df=3,  
                        max_df=0.5,
                        max_features=None,                 
                        ngram_range=(1, 2), 
                        use_idf=True, #enable inverse-document-frequency
                        smooth_idf=True,
                        stop_words = None)
                        
                        
            pd.read            
                        
# fit TF-IDF model 
tfvfit = tfv.fit(list(xtrain) + list(xtest))
xtrain_tfv =  tfvfit.transform(xtrain) 
xtest_tfv = tfvfit.transform(xtest)

filename = 'tfvfit.pkl'
pickle.dump(tfvfit, open(filename, 'wb'))


```

```{python}
#write transformed x and y into csv (unfinished)
transformed_test = pd.DataFrame(xtest_tfv, ytest)
transformed_test.to_csv(r'/Users/tinganlai/Documents/GitHub/PraticumProject-/rshiny/transformed_test.csv',  index=None, header=True)

```




```{python}
# train on logistic regression model
from sklearn.linear_model import LogisticRegression

clf = LogisticRegression(C=1.0,solver='lbfgs',multi_class='multinomial')
clf.fit(xtrain_tfv, ytrain)
predictions = clf.predict_proba(xtest_tfv)

aaa = clf.predict(xtest_tfv)
aaa
print (predictions)
print ("logloss: %0.3f " % multiclass_logloss(ytest, predictions))

```




### Save the model as pickle. We will use it in the shiny app
```{python}
import pickle 
  
# Save the trained model as a pickle string. 
# saved_model = pickle.dumps(clf) 
  
# save the model to disk
filename = 'finalized_model.pkl'
pickle.dump(clf, open(filename, 'wb'))
 

# Load the pickled model 
# lg_from_pickle = pickle.loads(saved_model) 
  
# Use the loaded pickled model to make predictions 
# lg_from_pickle.predict(xtest_tfv) 
```


```{python}
# load the model from disk
loaded_model = pickle.load(open(filename, 'rb'))
result = loaded_model.score(xtest_tfv, ytest)
print(result)

```



